Understanding Broadway Gross: Key Factors and Growth Strategies

### 2024-12-13 paper/paper.qmd
Update the typos in the paper

---
title: "Understanding Broadway Gross: Key Factors and Growth Strategies"
subtitle: "Optimizing Revenue Per Seat While Addressing Modest Holiday Gains and Revenue Declines in Tony Award Months"
author: "Xuanel Zhou"
thanks: "Code and data are available at: [Broadway_Gross](https://github.com/Isazhou13/Broadway_Gross)."
date: today
date-format: long
toc: true
abstract: "This study examines factors influencing weekly gross revenue on Broadway, focusing on key predictors such as average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months. A $1 increase in average ticket price adds $9,168 to weekly revenue, while an additional performance contributes $70,688, and each new seat generates $699.82, underscoring the importance of pricing and demand strategies over simply expanding seating capacity. Holiday weeks boost revenue by $16,684, but this modest increase relative to NYC’s tourism surge shows untapped potential for Broadway to enhance its appeal as a premier holiday destination. Conversely, Tony Award months are linked to a $7,140 decline in weekly revenue, highlighting the need to reposition the awards season as an industry-wide promotional opportunity to benefit all productions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here], scales [@scales], and modelsummary [@modelsummary]. The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets. **ggplot2** is used for data visualization, creating a range of plots to explore and present trends in the data. **knitr** facilitates the integration of analysis and reporting by generating dynamic reports in R Markdown. **arrow** is used for efficient handling of large datasets, particularly for reading and writing data in Parquet format to optimize storage and processing. The **here** package ensures reproducibility by standardizing file paths in the project directory, making it easier to locate and load data files. Finally, **scales** is employed to enhance the readability of plots by formatting axes, labels, and scales, ensuring clarity in the presentation of numeric and categorical data.

@@

However, converting real-world phenomena into publicly available dataset entries inevitably leads to the loss of important contextual details in such circumstances. For example, productions that include premium tickets or standing-room sales may disproportionately increase weekly grosses compared to those without these options. While the dataset includes a top ticket price metric, it does not specify the number of tickets sold at this price, leaving gaps in understanding revenue dynamics. Similarly, discounts and promotions, such as rush tickets or group sales, can lower the average ticket price, potentially underestimating the perceived value of tickets sold. Additionally, although the dataset includes weekly metrics, it does not specify whether performances took place on weekdays or weekends, limiting the analysis of gross patterns. These limitations underscore the challenges of translating complex industry data into simplified metrics for analysis.

@@

@fig-yearly captures the Broadway industry's growth over the decade. The yearly averages were calculated by averaging the weekly gross revenue across all Broadway shows for each year. The chart shows a steady increase in average yearly gross revenue, reflecting overall industry growth. From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2019. A slight dip in 2020 likely reflects the impact of the COVID-19 pandemic on Broadway operations.

@@

```
@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $300,000 to $2,000,000, which aligns with the results shown in @fig-weekly_gross. However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.

@@

# Generate a histogram for avg_ticket_price 
ggplot(analysis_data, aes(x = avg_ticket_price)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "black", alpha = 0.7) +  # Customize bin width and colors
  labs(
    x = "Average Ticket Price ($)",
    y = "Number of Occurrences"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )
```
@fig-avg_ticket_price shows the majority of average ticket prices are concentrated around $100, with a peak frequency between $80 and $120. The right skewed distribution, indicating that while most ticket prices are relatively affordable, there are instances of higher ticket prices extending beyond $300, with a few exceeding $500.

@@

```
@fig-performances highlights the consistency in Broadway’s performance schedules, with the vast majority of shows performing 8 times per week, reaching a frequency of over 10,000 occurrences. A small number of shows have fewer or occasionally more than 8 performances per week, likely due to special events, holidays, or production adjustments.

@@

The model results show that holiday weeks increase weekly gross revenue by an average of $16,684, reflecting a notable seasonal boost and aligning with expectations of higher audience availability during festive periods. Holiday weeks are a time when families often travel or plan special outings, and New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, bustling holiday markets, and the New Year’s Eve Ball Drop in Times Square. This festive atmosphere draws millions of tourists. However, the relatively modest increase of $16,684 per week suggests that Broadway may not be fully capitalizing on its unique position as a holiday destination. Studies on tourist behavior during holidays indicate that travelers are more inclined to seek unique and memorable experiences during festive periods [@pearce2013minds], creating a prime opportunity for Broadway to enhance its gross revenue and establish itself as a must-visit holiday experience.

@@

Thus, Broadway could transform the Tony Awards into an industry-wide promotional platform by adopting strategies that engage a broader audience and distribute the benefits more equitably, extending beyond just the nominated and award-winning productions. Collaborating with media outlets to produce exclusive behind-the-scenes content, interviews with nominees, and live coverage of performances from non-nominated shows could help expand the appeal of the awards season. Additionally, launching a "Broadway Awards Week" featuring discounted tickets, special packages, or unique experiences such as backstage tours could encourage attendance across multiple productions, leveraging the awards buzz to increase overall industry revenue. Centralized marketing campaigns highlighting the diversity and vibrancy of Broadway’s productions during this period could further enhance engagement and boost ticket sales across the ecosystem. By shifting the focus from individual winners to promoting the broader Broadway experience, the industry could transform the slight revenue decline during Tony Award months into a period of growth and shared success for all productions.

@@

Our sampling strategy utilizes ** simple random sampling** to ensure unbiased representation of Broadway audiences. This approach randomly selects participants from the overall population of Broadway ticket buyers and attendees, minimizing potential biases and ensuring the sample reflects the diversity of the audience.

@@

The survey will be implemented via **Google Forms**, which provids a cost-effective platform for data collection. You can access the survey at the following link: [Google Form Survey](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)

>>>>

---
title: "Understanding Broadway Gross: Key Factors and Growth Strategies"
subtitle: "Optimizing Revenue Per Seat While Addressing Modest Holiday Gains and Revenue Declines in Tony Award Months"
author: "Xuanel Zhou"
thanks: "Code and data are available at: [Broadway Gross](https://github.com/Isazhou13/Broadway_Gross)."
date: today
date-format: long
toc: true
abstract: "This study examines factors influencing weekly gross revenue on Broadway, focusing on key predictors including average ticket price, seating capacity, number of performances, holiday weeks, and Tony Award months. A $1 increase in average ticket price adds $9,168 to weekly revenue, while an additional performance contributes $70,688, and each new seat generates $699.82, underscoring the importance of pricing and demand strategies over simply expanding seating capacity. Holiday weeks boost revenue by $16,684, but this modest increase relative to NYC’s tourism surge shows untapped potential for Broadway to enhance its appeal as a premier holiday destination. Conversely, Tony Award months are linked to a $7,140 decline in weekly revenue, highlighting the need to reposition the awards season as an industry-wide promotional opportunity to benefit all productions."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

This study utilizes R packages [@citeR] for data cleaning and analysis, incorporating libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], arrow [@arrow], here [@here], scales [@scales], and modelsummary [@modelsummary].

The **tidyverse** package is employed for data manipulation, such as filtering, grouping, and reshaping datasets. **ggplot2** is used for data visualization, creating a range of plots to explore and present trends in the data. **knitr** facilitates the integration of analysis and reporting by generating dynamic reports in R Markdown. **arrow** is used for efficient handling of large datasets, particularly for reading and writing data in Parquet format to optimize storage and processing. The **here** package ensures reproducibility by standardizing file paths in the project directory, making it easier to locate and load data files. Finally, **scales** is employed to enhance the readability of plots by formatting axes, labels, and scales, ensuring clarity in the presentation of numeric and categorical data.

@@

However, converting real-world phenomena into publicly available dataset entries inevitably leads to the loss of important contextual details in such circumstances. For example, while the dataset includes a top ticket price metric, it does not specify the number of tickets sold at this price, making it challenging to fully understand revenue dynamics. Similarly, discounts and promotions, such as rush tickets or group sales, can lower the average ticket price, potentially underestimating the perceived value of tickets sold. Additionally, although the dataset includes weekly metrics, it does not specify whether performances took place on weekdays or weekends, limiting the analysis of gross patterns. These limitations underscore the challenges of translating complex industry data into simplified metrics for analysis.

@@

@fig-yearly captures the Broadway industry's growth over the decade. The yearly averages were calculated by averaging the weekly gross revenue across all Broadway shows for each year. It shows a steady increase in average yearly gross revenue, reflecting overall industry growth. From 2013 to 2015, revenues remain relatively stable, followed by sharp growth from 2016 onward, peaking in 2018.

@@

```
@fig-week_ending provides detailed information on weekly gross revenues, showing that most values clusters predominantly in the range of $300,000 to $2,000,000, which aligns with @fig-weekly_gross. However, there is a gradual upward trend in the maximum weekly gross over the years, indicating that the Broadway industry experienced growth during this period.

@@

# Generate a histogram for avg_ticket_price 
ggplot(analysis_data, aes(x = avg_ticket_price)) +
  geom_histogram(binwidth = 10, fill = "steelblue", color = "black", alpha = 0.7) +  # Customize bin width and colors
  labs(
    x = "Average Ticket Price ($)",
    y = "Number of Occurrences"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10)
  )
```
@fig-avg_ticket_price shows most average ticket prices are concentrated around $100, with a peak frequency between $80 and $120. The right skewed distribution, indicating that while most ticket prices are relatively affordable, there are instances of higher ticket prices extending beyond $300, with a few exceeding $500.

@@

```
@fig-performances highlights the consistency in Broadway’s performance schedules, with most shows performing 8 times per week, reaching a frequency of over 10,000 occurrences. A small number of shows have fewer or occasionally more than 8 performances per week, likely due to special events, holidays, or production adjustments.

@@

The model results show that holiday weeks increase weekly gross revenue by an average of $16,684, reflecting a notable seasonal boost and aligning with expectations of higher audience availability during festive periods. Holiday weeks are a time when families often travel or plan special outings, and New York City, home to Broadway, becomes a global attraction with iconic events like the Rockefeller Center Christmas Tree Lighting, bustling holiday markets, and the New Year’s Eve Ball Drop in Times Square. This festive atmosphere draws millions of tourists.

However, the relatively modest increase of $16,684 per week suggests that Broadway may not be fully capitalizing on its unique position as a holiday destination. Studies on tourist behavior during holidays indicate that travelers are more inclined to seek unique and memorable experiences during festive periods [@pearce2013minds], creating a prime opportunity for Broadway to enhance its gross revenue and establish itself as a must-visit holiday experience.

@@

Thus, Broadway could transform the Tony Awards into an industry-wide promotional platform by adopting strategies that engage a broader audience and distribute the benefits more equitably, extending beyond just the nominated and award-winning productions. Collaborating with media outlets to produce exclusive behind-the-scenes content, interviews with nominees, and live coverage of performances from non-nominated shows could help expand the appeal of the awards season.

Additionally, launching a "Broadway Awards Week" featuring discounted tickets, special packages, or unique experiences such as backstage tours could encourage attendance across multiple productions, leveraging the awards buzz to increase overall industry revenue. By shifting the focus from individual winners to promoting the broader Broadway experience, the industry could transform the slight revenue decline during Tony Award months into a period of growth and shared success for all productions.

@@

Our sampling strategy utilizes **simple random sampling** to ensure unbiased representation of Broadway audiences. This approach randomly selects participants from the overall population of Broadway ticket buyers and attendees, minimizing potential biases and ensuring the sample reflects the diversity of the audience.

@@

The survey will be implemented via **Google Forms**, which provids a cost-effective platform for data collection. You can access the survey at the following link: [Google Form - Broadway Audience Survey Form](https://docs.google.com/forms/d/e/1FAIpQLScAcdMoMbkOcOnZ_dPCV9xqiN-RMoCjisHEieW84dVjVMMiIA/viewform)
